Cosmological constraints from the redshift dependence of the galaxy angular 2-point correlation function

### 2016-08-31 draft/draft0.tex
updates

\begin{figure*}
   \centering{
   %\includegraphics[height=5.9cm]{fig8_0.eps}
   %\includegraphics[height=5.9cm]{fig8_wrongcos_0.eps}
   \includegraphics[width=16cm]{fig2.eps}
   }
   \caption{\label{fig_scatter}
  blah
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

@@

\begin{figure*}
   \centering{
%   \includegraphics[width=18cm]{fig9_0.eps}
%   \includegraphics[width=18cm]{fig9_1.eps}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}

   }
   \caption{\label{fig_cosmo}
   2pCF in cosmologies.
   }
\end{figure*}

@@

>>>>

\begin{figure*}
   \centering{
   %\includegraphics[height=5.9cm]{fig8_0.eps}
   %\includegraphics[height=5.9cm]{fig8_wrongcos_0.eps}
   %\includegraphics[width=16cm]{fig2.eps}
   \includegraphics[width=16cm,natwidth=8,natheight=14]{fig2.pdf}
   }
   \caption{\label{fig_scatter}
  blah
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

@@

@@

The same as \cite{Li2014,Li2015,Li2016} we need to correct for the redshift evolution of $r\xi$ caused by effects other than the wrongly assumed cosmological parameters.

Figure \ref{fig_diffz} already shows that, the growth of structure, especially in low redshift and on non-linear scales, 
changes the shape of $r\xi$ and caused relative enhancement on $r\lesssim2 h^{-1}\rm Mpc$.
So we limit the region of scale to $r>5h^{-1}\rm Mpc$ to minimize its effect.

Galaxies are biased tracers of dark matter field, 
and more massive galaxies tend to reside in regions with higher density contrast.
So in large scale structure surveys the bias of the galaxy sample is an important fator which has large effect on the clustering properties of the sample.
The upper panels of Figure \ref{fig_sys} displays five set of galaxy samples in a $3175\times3175\times105$ $(h^{-1}\rm Mpc)^3$ volume, taken from the $z=0$ snapshots data.
Different lower mass limits of $3\times 10^{11} M_{\odot}$, $3\times 10^{11} M_{\odot}$, $3\times 10^{11} M_{\odot}$ and $3\times 10^{11} M_{\odot}$
are imposed to create subsamples with different galaxy bias, 
and the measured angular 2pCF are displayed.
The different mass cuts result in large variation in the amplitude of the 2pCF (left panel),
while the shape of the 2pCF remains less affected (middle panel).
Compared with the sample with mass cut $M>3\times 10^{11} M_{\odot}$,
samples with mass limit $3\times 10^{11} M_{\odot}$, $3\times 10^{11} M_{\odot}$ and $3\times 10^{11} M_{\odot}$
have the amplitude of 2pCFs enhanced by $10\%,\ 50\%$ and $100\%$,
while the change in $\hat{r\xi}$ is only $0.5\%,\ 2\%$ and $4\%$.
Considering the very large change in the mass cut,
the change in the shape of 2pCF is not significant.

The galaxy peculiar velocity contribute to the observed galaxy redshift and distorted the galaxy radial position in redshift space,
known as the redshift space distortion (RSD).
It is the major source of systematics for our analysis of \cite{Li2014,Li2015,Li2016}, where the 3D galaxy distribution is utilized to derive cosmological constraint.
In this analysis its effect becomes much milder since the angular positions of the galaxies is not affected by RSD at all.
But it still affects our analysis in the procedure of preparing the subsamples of galaxies for 2pCF analysis.
The galaxies observed in a survey are split into shells of subsamples, with different redshift ranges, to get the 2pCF at different redshifts.
RSD disortes the galaxy redshift and as a result some galaxies close the boundaries of shells will be distributed to wrong redshift shells.

The lower panel of Figure \ref{fig_sys} displays the RSD effect on 2pCF.
To mimick the effect of RSD we shift the $Z$ coordinates of galaxies according to the relation 
\begin{equation}\label{eq:zvpeu}
\Delta z = (1+z) \frac{v_{{\rm Z}}}{c},
\end{equation}
where $v_{{\rm Z}}$ is the galaxy peculiar velocity in $Z$ direction.
Then we split the whole box into 30 slices with thickness $105h^{-1}\rm Mpc$, 
and measure the angular 2pCF.
The left panel shows that the amplitude of measured 2pCF is enhanced by $\sim 10\%$ in case of considering the RSD effect on spliting samples.
The middle panel shows that the shape of 2pCF is also altered -- the slop is suppressed.
If looking at the redshift evolution,
the curves $\hat{r\xi} - \hat{r\xi}(z=0)$ displayed in the right panel,
they changed a lot compared with the case of no RSD effect (the right panel of Figure \ref{fig_diffz}),
but do not become much larger. %But RSD effect does not introduce large redshfit evolution, although the shape of  is

Another effect is redshfit errors ...
Especially large in photometric surveys...

One shall construct reliable mock surveys to correct the systematic effects ...

%The outer boundary of the mock survey becomes fuzzy due to the peculiar velocity effect 
%on the galaxy redshifts (Eq. (\ref{eq:zvpeu})).
%A population of galaxies, that are expected to enter the $z<0.7$ region from the outside, is missing.
%(these $z>0.7$ galaxies have a peculiar velocity toward us and 
%their observed redshfits become lower than 0.7).
%To avoid this problem we set the maximal redshift at 0.693, 
%23.3 $h^{-1}{\rm Mpc}$ away from $z=0.7$.

%3.000e11', '1.000e12', '4.000e12',  '1.000e13
